---
title: "Response Variable"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
bibliography: ../report/references.bib
csl: ../report/elsevier-harvard.csl
---


```{r setup, include = FALSE}
source("../code/workflowr-utils.R")
```

# Units of analysis

Two different units of analysis are tested against their capability
to capture environmental processes contributing to the occurrences of
violent conflict. The first unit of analysis represents NUTS-3 Level
of administrative units over the African continent.

```{r read-adm}
adm = st_read("../data/vector/states_mask.gpkg", quiet = T)
adm = adm[,c("adm1_code", "adm1_code", "name", "name_de", "name_en", "type_en",
             "latitude", "longitude", "sov_a3", "adm0_a3", "geonunit")]
adm
```

As we can see from above output, we end up with 847 features in total covering
the African continent. Let's plot a map which's color is based on the country
a certain polygon belongs to. The results should look quite familiar:

```{r plot-adm}

adm %<>%
  st_make_valid() %>%
  st_cast("MULTIPOLYGON") %>%
  mutate(area = st_area(geom))

adm %>%
  group_by(sov_a3) %>%
  summarise(geom = st_union(geom), area = sum(area)) %>%
  st_centroid() -> adm_point

tmap_options(max.categories = 50)

tm_shape(adm) +
  tm_polygons("sov_a3", border.col = "white", lwd = .5) +
  tm_shape(adm_point) +
  tm_text("sov_a3", size = "area") +
  tm_legend(show = FALSE)

```

In comparison to administrative units we test the capability of sub-basin watersheds
to capture the pattern of violent conflicts. The selection of the appropriate
level was mainly driven to obtain a comparable number of units in order to not 
include a bias by diverging sizes. Thus the fifth level of the Hydrosheds datasets
was chosen.

```{r read-basins}
bas = st_read("../data/vector/basins_mask.gpkg", quiet = TRUE)
bas
```
The total number of units is 1013 which is roughly comparable to the number of
administrative units. On a map we get a less familiar pattern of the African 
continent, however, we can distinguish between the main watersheds.

```{r plot-bas}
bas_group = st_read("../data/raw/hydrosheds/hybas_af_lev03_v1c.shp", quiet = TRUE)
bas_group %<>% 
  mutate(HYBAS_ID = as.factor(HYBAS_ID))

bas %<>%
  mutate(area = st_area(geom))

tm_shape(bas_group) +
  tm_polygons("HYBAS_ID", lwd = 0) +
  tm_shape(bas) +
  tm_borders("white", lwd = .3) +
  tm_legend(show = FALSE)
```

The next plot shows a comparison of the distribution of area size between the 
two different units of analysis. The average area size of the sub-basin watersheds
is slightly higher compared to the administrative units. However, for both
types of units the majority of individuals lie in a comparable range. For administrative
units there are both more small as well as very large units. Overall, the size
of the units remains comparable between the two. 

```{r comp-area}

data = data.frame(group = c(rep("ADM", nrow(adm)), rep("BAS", nrow(bas))), 
                  area = c(as.numeric(adm$area / 1000000), as.numeric(bas$area / 1000000)))

ggplot(data) +
  geom_boxplot(aes(y=area, group=group, fill=group)) +
  labs(fill = "unit of analysis", y="Area [km²]") +
  theme_classic() +
  scale_y_continuous(labels = scales::comma) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```

# Conflict data

We use data from the Upsala conflict data program to retrieve the response variable
for this project. The database is an event database, meaning that every reported
violent conflict with at least one death is included as an single event associated
with information on involved actors, time and location as well as estimated deaths
by party involved. Since the data is mainly collected automatically sometimes
inaccuracies concerning the exact location or the number of deaths are introduced.
However, the data creators include information on the accuracy and thus the reliablity
for each logged event.
We downloaded the database for the African continent and filtered it to events 
occurring between 2000 and 2019 and additionally only included events for which
the quality of the geographic localization was at least accurate on the sub-national
level and the accuracy of the time was at least on a monthly scale.
Additionally, the data is provided with three different classes of conflict which
were extracted as well. These are state-based violence, non-state violence and 
one-sided violence.

```{r load-response}
load("../data/raw/ged/ged201.RData")
ged201$date_start = as.Date(ged201$date_start, "%Y/%m/%d")
ged201 = st_as_sf(ged201, coords =  c("longitude", "latitude"), crs = "EPSG:4326")
ged201 = ged201[which(st_intersects(st_union(adm), ged201, sparse = FALSE)), ]

ged201 %>%
  as_tibble() %>%
  mutate(date_start =  as.Date(date_start, "%Y/%m/%d")) %>%
  filter(date_start > as.Date("1999-12-31"), 
         where_prec %in% c(1,2,3),
         date_prec != 5) %>%
  select(type_of_violence, date_start, starts_with("deaths_"), country, geometry) -> response_raw
response_raw
```
In total we obtained 86,377 distinct events coupled with the filtering explained above.
The diagram below indicates the distribution of these events over the time period
on a monthly scale.


```{r response-dist}
response_raw %>%
  mutate(month = zoo::as.yearmon(date_start),
         type_of_violence = factor(type_of_violence, labels = c("state-based", "non-state", "one-sided"))) %>%
  group_by(month, type_of_violence) %>%
  summarise(count = n()) %>%
  complete(month, type_of_violence, fill = list(count = 0)) -> data 

ggplot(data) +
  geom_bar(aes(y=count, x=month, fill = type_of_violence), stat = "identity") +
  theme_classic() +
  labs(y="Number of events", x="Time", fill="Type of violence") +
  theme(legend.position="bottom")
```
We can assume an increasing trend in the number of events over the time period. Also,
the percentage of non-state violence increases over time, mainly to the cost of one-sided 
violence. We also can observe some kind of seasonal cycle in the number of conflicts.
In order to verify these assumptions we can conduct a decomposition of the time-series.
We firstly do so for the total number of events and then we conduct the same analysis
by type.

```{r dec-all}
response_raw %>%
  mutate(month = zoo::as.yearmon(date_start),
         type_of_violence = factor(type_of_violence, labels = c("state-based", "non-state", "one-sided"))) %>%
  group_by(month) %>%
  summarise(count = n())  -> ts_data
ts_data = ts(ts_data$count, start = c(2000,1), frequency = 12)
dec = decompose(ts_data)

data = data.frame(obsv = as.numeric(dec$x),
                  seasonal = as.numeric(dec$seasonal),
                  trend =  as.numeric(dec$trend),
                  random = as.numeric(dec$random),
                  date = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month"))

data %>%
  as_tibble() %>%
  gather(component, value, -date) %>%
  mutate(component = factor(component, levels = c("obsv", "trend", "seasonal", "random"))) %>%
  ggplot() +
  geom_line(aes(x=date, y=value), color = "royalblue3") +
  facet_wrap(~component, nrow = 4, scales = "free_y") +
  theme_classic() +
  labs(y = "Value", x = "Time")

```
Concerning the decomposition of all types of violence combined we observe an 
unsteady trend pattern from 2000 to 2010, but a substantial increase afterwards. 
In 2014 the trend stabilizes at a high level. The seasonality of the data is quite 
strong, with a peak in January and a period with low occurrences between August 
and December.

```{r dec-type}
response_raw %>%
  mutate(month = zoo::as.yearmon(date_start),
         type_of_violence = factor(type_of_violence, labels = c("state-based", "non-state", "one-sided"))) %>%
  group_by(month, type_of_violence) %>%
  summarise(count = n()) %>%
  complete(month, type_of_violence, fill = list(count = 0))-> ts_data2

dec_types = lapply(c("state-based", "non-state", "one-sided"), function(x){
  ts_data2 %>%
    filter(type_of_violence == x) %>%
    pull(count) %>%
    ts(start = c(2000,1), frequency = 12) %>%
    decompose() 
})

names(dec_types) = c("state-based", "non-state", "one-sided")

plt_data = lapply(c("state-based", "non-state", "one-sided"), function(x){
  tmp  = dec_types[[x]]
  tmp = data.frame(type = x,
                   obsv = as.numeric(tmp$x),
                   seasonal = as.numeric(tmp$seasonal),
                   trend =  as.numeric(tmp$trend),
                   random = as.numeric(tmp$random),
                   date = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month"))
  tmp
})

plt_data = do.call(rbind, plt_data)

plt_data %>%
  as_tibble() %>%
  gather(component, value, -type, -date) %>%
  mutate(component = factor(component, levels = c("obsv", "trend", "seasonal", "random")),
         type = factor(type, levels = c("state-based", "non-state", "one-sided"))) %>%
  ggplot() +
  geom_line(aes(x=date, y=value, color=type)) +
  facet_wrap(~component, nrow = 4, scales = "free_y") +
  theme_classic() +
  labs(y = "Value", x = "Time", color = "Type of violence") +
  theme(legend.position="bottom")

```

When we analyse the decomposition based on types of conflicts, we see that state-based
violence is dominating the overall pattern. By far the most conflicts belong to that
class and the seasonal and trend pattern of all classes combined mainly mirrors 
the dynamic found for state-based violence. 
The patterns for non-state and one-sided violence are quite distinct from the
former class, however, the two are very much alike. The seasonal pattern shows
that the lowest number of conflicts are found from September through December while
the peak number of conflicts is found in January. Concerning the trend, one-sided
violence overall is rather stable over the time period. After 2005 there is a steady
increase in non-state violence which increases substantially in slope with the year 2017.

Aside from the count of events, we can analyze the number of casualties which were
suffered when the events occurred. As pointed out before, the casualties are ordered
by participating groups and additionally deaths of civilians and unknown deaths are
included in the database. Here we will focus on the total number of deaths, irrespective
of the group affiliation.

```{r deaths-hist}
response_raw %>%
  mutate(month = zoo::as.yearmon(date_start),
         type_of_violence = factor(type_of_violence, labels = c("state-based", "non-state", "one-sided"))) %>%
  group_by(month, type_of_violence) %>%
  summarise(deaths = sum(deaths_civilians, deaths_a, deaths_b, deaths_unknown)) %>%
  complete(month, type_of_violence, fill = list(deaths = 0))-> deaths_dat

deaths_dat %>%
  group_by(month) %>%
  #summarise(deaths = sum(deaths)) %>%
  ggplot() +
  geom_histogram(aes(x=deaths, group = type_of_violence, color = type_of_violence, fill = type_of_violence), 
                 alpha=0.5, position="stack", binwidth = 50)+
  theme_classic() +
  labs(y="Count", x="Number of casualties", color = "Type of violence", fill = "Type of violence") +
  theme(legend.position = "bottom")

```

The histogram of the number of casualties reveals that one-sided and state-based 
violence generally are associated with numbers of casualties
below 1000. State-based violence on the other hand clearly is the most frequent
violence class with casualties higher 1000.

```{r deaths-ts}
deaths_dat %>%
  ggplot() +
  geom_bar(aes(y=deaths, x=month, fill = type_of_violence), stat = "identity") +
  theme_classic() +
  labs(y="Number of casulties", x="Time", fill="Type of violence") +
  theme(legend.position="bottom")
```
Concerning the dynamic of casualties over time, we can observe relatively high
numbers of casualties at the beginning of the time series with a low episode around
from 2005 to 2010. Starting with 2011, the casualties seem to increase and the
number of casualties reaches its highest level of the complete time series between
2014 and 2015. There is a small decrease towards the year 2018.

```{r deaths-dec}
deaths_dat %>%
  group_by(month) %>%
  summarise(deaths = sum(deaths)) %>%
  pull(deaths) %>%
  ts(start = c(2000,1), frequency = 12) %>%
  decompose() -> dec

data = data.frame(obsv = as.numeric(dec$x),
                  seasonal = as.numeric(dec$seasonal),
                  trend =  as.numeric(dec$trend),
                  random = as.numeric(dec$random),
                  date = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month"))

data %>%
  as_tibble() %>%
  gather(component, value, -date) %>%
  mutate(component = factor(component, levels = c("obsv", "trend", "seasonal", "random"))) %>%
  ggplot() +
  geom_line(aes(x=date, y=value), color = "royalblue3") +
  facet_wrap(~component, nrow = 4, scales = "free_y") +
  theme_classic() +
  labs(y = "Value", x = "Time")
```

The general trend irrespective of the violent type shows a flat dynamic from
2005 to 2010. After that year the slope of the frend increases substantially resulting
in the highest peak between 2014 and 2015 which remains on a relativly high level
even towards 2018. The seasonality of casualties is quite similar to the total number of 
events, namely with a bimodal peak in March and May. The month with the lowest
numbers of casualties is November.


```{r deaths-dec-type}
deaths_dec = lapply(c("state-based", "non-state", "one-sided"), function(x){
  deaths_dat %>%
    filter(type_of_violence == x) %>%
    pull(deaths) %>%
    ts(start = c(2000,1), frequency = 12) %>%
    decompose() 
})

names(deaths_dec) = c("state-based", "non-state", "one-sided")

plt_data = lapply(c("state-based", "non-state", "one-sided"), function(x){
  tmp  = deaths_dec[[x]]
  tmp = data.frame(type = x,
                   obsv = as.numeric(tmp$x),
                   seasonal = as.numeric(tmp$seasonal),
                   trend =  as.numeric(tmp$trend),
                   random = as.numeric(tmp$random),
                   date = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month"))
  tmp
})

plt_data = do.call(rbind, plt_data)

plt_data %>%
  as_tibble() %>%
  gather(component, value, -type, -date) %>%
  mutate(component = factor(component, levels = c("obsv", "trend", "seasonal", "random")),
         type = factor(type, levels = c("state-based", "non-state", "one-sided"))) %>%
  ggplot() +
  geom_line(aes(x=date, y=value, color=type)) +
  facet_wrap(~component, nrow = 4, scales = "free_y") +
  theme_classic() +
  labs(y = "Value", x = "Time", color = "Type of violence") +
  theme(legend.position="bottom")
```
Unsurprisingly, the general time-series is dominated by the signal of state-based violence
as well.
However, the seasonality of casualties for the different types of violence are more 
alike than compared to the total number of events. The local peak during the years
2008 to 2009 is not observed in non-state and one-sided violence. The same is true
for non-state violence where there is no substantial increase in casualties in 2014.
The increase is observed with one-sided violence, however, the trend flips shortly
after 2015 showing a greater stability than compared with state-based violence.

# Combining response with units of analysis

Until now the analysis of violent conflict took a perspective on the African
continent as a whole. Since the overall aim of this project is to establish a 
machine learning model to predict violent conflict for smaller spatial units, 
a spatio-temporal aggregation of the conflict data is needed. 
To achieve this, in the first step we declare a spatio-temporal objects based 
on the spatial information of the units of analysis. We will need the package 
`spacetime` for this.

```{r st-units}
library(spacetime)
date_vec = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month")

adm_st = STF(as_Spatial(adm), date_vec)
bas_st = STF(as_Spatial(bas), date_vec)
str(bas_st@time)
```

As evident from the above output these objects now contain a time slot where 
the information on the time dimension is stored. We specified a monthly resolution
from January 2000 to December 2019. 
The next step is to aggregate the conflict data based on their location in space
and time and add the data to the objects declared above. Note, that we are aggregating
the total sum of deaths irrespective of the classification but we want to keep
information on the type of violence. Therefor the raw data is in need for some
restructuring.


```{r st-aggregate, eval=FALSE}
response_raw %>% 
  mutate(deaths = deaths_civilians + deaths_a + deaths_b + deaths_unknown) %>%
  select(type_of_violence, date_start, deaths, geometry) -> agg_data 
classes = c("sb", "ns", "os", "all")

for(i in 1:4){ # loop through types of conflict + all types
  print(i)
  if(i != 4){ # filter if appropriate
    points = as_Spatial(st_as_sf(agg_data[agg_data$type_of_violence == i, ]))
  } else { # else take all conflicts
    points = as_Spatial(st_as_sf(agg_data)) 
  }
  # declaration of a space-time data frame
  points_st = STIDF(points, points$date_start, data = data.frame(casualties = points$deaths))
  # aggregate the sum of deahts
  res_adm = aggregate(points_st, adm_st, sum, na.rm = T)
  saveRDS(res_adm, paste0("../data/vector/ged/st_adm_", classes[i],".rds"))
  rm(res_adm)
  gc()
  print("Done with ADM.")
  res_bas = aggregate(points_st, bas_st, sum, na.rm = T)
  saveRDS(res_bas, paste0("../data/vector/ged/st_bas_", classes[i],".rds"))
  rm(res_bas)
  gc()
  print("Done with BAS.")
}
```

## Read and write to GPKG.

```{r eval=FALSE}
bas_data = list.files("../data/vector/ged/", pattern ="bas", full.names = T)
adm_data = list.files("../data/vector/ged/", pattern ="adm", full.names = T)

for(x in bas_data){
  object = readRDS(x)
  object@data[is.na(object@data)] = 0 # set NA to 0 for no conflict
  object = as(object, "Spatial")
  object = st_as_sf(object)
  st_crs(object) = st_crs(4326)
  type = str_remove(str_split(basename(x), "_")[[1]][3], ".rds")
  names(object)[1:(ncol(object)-1)] = format(as.Date(names(object)[1:(ncol(object)-1)]), "%b-%Y")
  st_write(object, paste0("../data/vector/response_", type, "_basins.gpkg"), delete_dsn = T)
}

for(x in adm_data){
  object = readRDS(x)
  object@data[is.na(object@data)] = 0 # set NA to 0 for no conflict
  object = as(object, "Spatial")
  object = st_as_sf(object)
  st_crs(object) = st_crs(4326)
  type = str_remove(str_split(basename(x), "_")[[1]][3], ".rds")
  names(object)[1:(ncol(object)-1)] = format(as.Date(names(object)[1:(ncol(object)-1)]), "%b-%Y")
  st_write(object, paste0("../data/vector/response_", type, "_states.gpkg"), delete_dsn = T)
}
```

```{r}
files = list.files("../data/vector/", pattern = "response", full.names = T)

results = list()
for(i in c("basins", "states")){
  tmp_files  = files[grep(i, files)]
  levels = sapply(tmp_files, function(x) str_split(basename(x), "_")[[1]][2], USE.NAMES = F)
  data = do.call(rbind, lapply(1:length(tmp_files), function(x){
    tmp_files[x] %>%
      st_read(quiet=T) %>%
      st_drop_geometry %>%
      mutate(id = 1:n()) %>%
      gather("time", "value", -id) %>%
      mutate(type = levels[x])
  })
  )
  results[[i]] = data
}

```

## Unbalanced Data set

```{r}
results$basins %>%
  as_tibble() %>%
  mutate(conflict = if_else(value>0, "yes", "no")) %>%
  count(conflict) -> n_bas

results$states %>%
  as_tibble() %>%
  mutate(conflict = if_else(value>0, "yes", "no")) %>%
  count(conflict) -> n_adm

dat = data.frame(unit = c("states", "basins"), perc = c(n_adm$n[n_adm$conflict=="yes"]/n_adm$n[n_adm$conflict=="no"]*100,
                                                        n_bas$n[n_bas$conflict=="yes"]/n_bas$n[n_bas$conflict=="no"]*100))

ggplot(dat) +
  geom_bar(aes(x=unit, y=perc, fill=unit), color = "white", stat="identity", width = .5) +
  theme_classic() +
  labs(x="", y="Percentage of conflict district-months", fill="Unit of analysis")
```
```{r}
results$basins$unit = "basin"
results$states$unit = "states"

data = as_tibble(do.call(rbind, results))

data %>%
  #filter(type == "all") %>%
  mutate(conflict = if_else(value>0, "yes", "no")) %>%
  group_by(id, unit, type) %>%
  summarise(conflict = sum(conflict == "yes"), deaths = sum(value)) %>%
  ggplot() +
  geom_point(aes(x=conflict, y=deaths, color=unit), alpha=.4) +
  facet_wrap(~type) +
  theme_classic() +
  labs(y="Number of casualties", x="Number of district-months with conflict",
       color="Unit of analysis")
```

```{r}
data %>%
  #filter(type == "all") %>%
  mutate(conflict = if_else(value>0, "yes", "no")) %>%
  group_by(unit, type, time) %>%
  summarise(conflict = sum(conflict == "yes"), deaths = sum(value)) %>%
  ggplot() +
  geom_line(aes(x=time, y=conflict, color=unit, group=unit), alpha=.6) +
  facet_wrap(~type) +
  theme_classic() +
  labs(y="Number of districts with conflict", x="Time",
       color="Unit of analysis") +
  theme(axis.ticks.x=element_blank(),
        axis.text.x=element_blank())
```

# Spatial Pattern


```{r}
data %>%
  #filter(type == "all") %>%
  mutate(conflict = if_else(value>0, "yes", "no")) %>%
  group_by(id, unit, type) %>%
  summarise(conflict = sum(conflict == "yes"), deaths = sum(value)) %>%
  ungroup() %>%
  group_split(unit) -> g_data
names(g_data) = c("basin", "states")

adm$id = 1:nrow(adm)
bas$id = 1:nrow(bas)

adm = left_join(adm, g_data$states)
bas = left_join(bas, g_data$basin)

```

```{r map-adm-deaths}
tm_shape(adm) +
  tm_polygons(col = "deaths", palette = "-RdYlBu", breaks = c(0,10,50,100,500,1000,2000,4000,6000,8000,10000,+Inf), border.col = "gray", lwd = .5) +
  tm_facets("type")
```
```{r map-adm-conficts}
tm_shape(adm) +
  tm_polygons(col = "conflict", palette = "-RdYlBu", breaks = c(0,5,10,25,50,75,100,150,+Inf), border.col = "gray", lwd = .5) +
  tm_facets("type")
```


```{r map-bas-deaths}
tm_shape(bas) +
  tm_polygons(col = "deaths", palette = "-RdYlBu", breaks = c(0,10,50,100,500,1000,2000,4000,6000,8000,10000,+Inf), border.col = "gray", lwd = .5) +
  tm_facets("type")
```


```{r map-bas-conficts}
tm_shape(bas) +
  tm_polygons(col = "conflict", palette = "-RdYlBu", breaks = c(0,5,10,25,50,75,100,150,+Inf), border.col = "gray", lwd = .5) +
  tm_facets("type")
```
