---
title: "Precipitation Anomalies"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
bibliography: ../report/references.bib
csl: ../report/elsevier-harvard.csl
---

```{r setup, include=FALSE}
source("../code/workflowr-utils.R")
```

# Loading the data

```{r read-data}
files = list.files("../data/vector/extraction/", pattern = "ANOM", full.names = T)

data = lapply(files, function(x){
  filename = str_split(basename(x), "_")[[1]]
  if(length(filename) == 3){
    unit = filename[1]
    buffer = as.numeric(filename[2])
    var = str_remove(filename[3], ".gpkg")
  } else {
    unit = filename[1]
    buffer = 0
    var =  str_remove(filename[2], ".gpkg")
  }
  
  layers = ogrListLayers(x)
  layers = layers[grep("attr_", layers)]
  data = do.call(cbind, lapply(layers, function(l){
    tmp = st_read(x, layer = l, quiet = TRUE)
    names(tmp) = l
    tmp
  }))
  
  data$id = 1:nrow(data)
  data %>%
    as_tibble() %>%
    mutate(unit = unit, buffer = buffer, var = var) %>%
    gather("time", "value", -id, -unit, -buffer, -var) %>%
    mutate(time = str_remove(time, "attr_"))
})

data = do.call(rbind, data)
str(data)
```

# Missing Values

The resulting dataframe contains roughly 1.8 Mio. rows containing the district-month
observations for the two different units of analysis as well as the buffered data.
Let's start looking at the unbuffered data.


```{r na-analysis}
data %>%
  group_by(unit, buffer) %>%
  summarise(N = n(), isna = sum(is.na(value)), isnotna = sum(!is.na(value)), perc = sum(is.na(value)) / n() * 100)
```

# Time Series

```{r time-series}
data %>%
  filter(buffer==0) %>%
  mutate(time = as.Date(paste0(time, "-01"))) %>%
  group_by(time, unit) %>%
  summarise(value = mean(value, na.rm = T)) %>%
  ggplot() +
  geom_line(aes(x=time, y=value, color = unit)) +
  theme_classic() +
  labs(y="Precipitation [mm]", x = "Time", color = "Unit of Analysis")

```

# Seasonal decompositon

```{r decompositon}
data %>%
  filter(unit == "basins", buffer == 0) %>%
  mutate(time = as.Date(paste0(time, "-01"))) %>%
  group_by(time) %>%
  summarise(value = mean(value, na.rm = T)) %>% 
  pull(value) %>%
  ts(start = c(2000,1), frequency = 12) %>%
  decompose() -> dec_basins

data %>%
  filter(unit == "states", buffer == 0) %>%
  mutate(time = as.Date(paste0(time, "-01"))) %>%
  group_by(time) %>%
  summarise(value = mean(value, na.rm = T)) %>% 
  pull(value) %>%
  ts(start = c(2000,1), frequency = 12) %>%
  decompose() -> dec_states
dec_data = list(basins = dec_basins, states = dec_states)

dec_data = lapply(c("basins", "states"), function(x){
  tmp = dec_data[[x]]
  data.frame(type = x,
             obsv = as.numeric(tmp$x),
             seasonal = as.numeric(tmp$seasonal),
             trend =  as.numeric(tmp$trend),
             random = as.numeric(tmp$random),
             date = seq(as.Date("2000-01-01"), as.Date("2019-12-31"), by = "month"))
  
})

dec_data = do.call(rbind, dec_data)

dec_data %>%
  as_tibble() %>%
  gather(component, value, -type, -date) %>%
  mutate(component = factor(component, levels = c("obsv", "trend", "seasonal", "random"))) %>%
  ggplot() +
  geom_line(aes(x=date, y=value, color=type)) +
  facet_wrap(~component, nrow = 4, scales = "free_y") +
  theme_classic() +
  labs(y = "Precipitation [mm]", x = "Time", color = "Unit of Analysis") +
  theme(legend.position="bottom")
```

# Auto-correlation Analysis

```{r acf-data}
data %>%
  filter( buffer == 0) %>%
  mutate(time = as.Date(paste0(time, "-01"))) %>%
  group_by(unit, time) %>%
  summarise(value = mean(value, na.rm = T)) %>%
  spread(key = unit, value = value) -> acf_data
```

## States

```{r acf-states}
acf(acf_data$states, lag.max = 24)
```

## Basins

```{r acf-basins}
acf(acf_data$basins, lag.max = 24)
```

# Spatial Pattern

```{r spatial-join}
poly_bas = st_read("../data/vector/basins_mask.gpkg", quiet = T)
crs <- st_crs("EPSG:3857")
poly_bas <- st_transform(poly_bas, crs)
poly_bas <- st_simplify(poly_bas, dTolerance = 1000, preserveTopology = T)
poly_bas$id = 1:nrow(poly_bas)
poly_adm = st_read("../data/vector/states_mask.gpkg", quiet = T)
poly_adm <- st_transform(poly_adm, crs)
poly_adm <- st_simplify(poly_adm, dTolerance = 1500, preserveTopology = T)
poly_adm$id = 1:nrow(poly_adm)



data %>%
  filter(buffer == 0) %>%
  mutate(time = as.Date(paste0(time, "-01")),
         month = month(time)) %>%
  group_by(unit, id, month) %>%
  summarise(obsv = sum(is.na(value))) -> obs_data


data %>%
  filter(buffer == 0) %>%
  mutate(time = as.Date(paste0(time, "-01")),
         month = month(time)) %>%
  group_by(unit, id, month) %>%
  summarise(value = mean(value, na.rm = T)) -> sum_data

poly_adm = left_join(poly_adm, filter(sum_data, unit == "states"))
poly_bas = left_join(poly_bas, filter(sum_data, unit == "basins"))
poly_adm = left_join(poly_adm, filter(obs_data, unit == "states"))
poly_bas = left_join(poly_bas, filter(obs_data, unit == "basins"))

```

## Administrative Units by month

### Number of missing observations

```{r map-states-obsv}
tm_shape(poly_adm) +
  tm_polygons("obsv", palette = "-RdBu", border.col = "white", lwd = .5) +
  tm_facets("month")
```
### Precipitation map

```{r map-states-value}
tm_shape(poly_adm) +
  tm_polygons(col = "value", palette = "RdYlBu", breaks = c(-Inf,-30,-20,-10,0,10,20,30,+Inf), border.col = "white", lwd = .5) +
  tm_facets("month")
```

## Sub-basin watersheds by month

### Number of missing observations

```{r map-basins-obsv}
tm_shape(poly_bas) +
  tm_polygons("obsv", palette = "-RdBu", border.col = "white", lwd = .5) +
  tm_facets("month")
```

### Precipitation map

```{r map-basins-value}
tm_shape(poly_bas) +
   tm_polygons(col = "value", palette = "RdYlBu", breaks = c(-Inf,-30,-20,-10,0,10,20,30,+Inf), border.col = "white", lwd = .5) +
  tm_facets("month")
```






